---
title: "R Notebook"
author: "Toni Moreno from Bibliometrix"
date: "1/10/2021"
output: html_document
---

# Stable version from CRAN (Comprehensive R Archive Network)
# if you need to execute the code, remove # from the beginning of the next line

# install.packages("bibliometrix")


# Most updated version from GitHub
# if you need to execute the code, remove # from the beginning of the next lines

# install.packages("devtools")
# devtools::install_github("massimoaria/bibliometrix")



```{r setup, include=FALSE}
library(bibliometrix)

knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading txt or bib files into R environment
#  "http://bibliometrix.org/datasets/joi.txt"

# Converting the loaded files into a R bibliographic dataframe
Ms <- convert2df(file.choose(), dbsource="isi",format="plaintext")

M <- dplyr::full_join(M,Ms)
rm(Ms)
```

```{r}
#options(width=160)
results <- biblioAnalysis(M)
summary(results, k=10, pause=F, width=130)
```


```{r}
plot(x=results, k=10, pause=F)
```

```{r}
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:20])
```

```{r}
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
net=networkPlot(NetMatrix, n = 50, Title = "Co-Citation Network", type = "fruchterman", size.cex=TRUE, size=20, remove.multiple=FALSE, labelsize=0.7,edgesize = 10, edges.min=5)
```

```{r}
#netstat <- networkStat(NetMatrix)
#summary(netstat,k=10)
```

Journal (Source) co-citation analysis

```{r}
M=metaTagExtraction(M,"CR_SO",sep=";")
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "sources", sep = ";")
net=networkPlot(NetMatrix, n = 50, Title = "Co-Citation Network", type = "auto", size.cex=TRUE, size=15, remove.multiple=FALSE, labelsize=0.7,edgesize = 10, edges.min=5)
```

Descriptive analysis of Journal co-citation network characteristics


```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=10)
```

Section 3: Historiograph - Direct citation linkages

```{r}
histResults <- histNetwork(M, min.citations=quantile(M$TC,0.75), sep = ";")
```

```{r}
options(width = 130)
net <- histPlot(histResults, n=20, size.cex=TRUE, size = 5, labelsize = 3, arrowsize = 0.5)
```


